Outstanding Title

### 2017-04-17 writing/EpiDraft.Rmd
Use purrr to scrape 2017 weeks 1-9

>>>>

```{r}
#scrape just the New York City value for week 14 of 2017 from cdc website:
library(rvest)
url <- read_html("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=14&mmwr_table=2J&request=Submit&mmwr_location=")
#Used Selector Gadget to get css selector
nyc <- html_nodes(url, 'tr:nth-child(15) td:nth-child(2)')
as.numeric(html_text(nyc))

#Use purrr to get values for 2017 weeks 1-9
i <- 1:9
url <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=0", as.character(.x), "&mmwr_table=2J&request=Submit&mmwr_location=", sep=""))
html <- url %>% map(~read_html(.x))
nodes <- html %>% map(~html_nodes(.x, 'tr:nth-child(15) td:nth-child(2)'))
nycdat <- nodes %>% map(~html_text(.x))
as.numeric(nycdat)

#There was no table for week 2 so we have an NA.
```
